draft_final_assignment

### 2022-11-28 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

```{r}
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
```

@@

##Creatung a dfm from the corpus
```{r }
dfm_corp <- corp %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used"))%>%
  dfm()
```

##Most common words in the corpus
```{r}

dfm_corp %>% colSums() %>% sort(decreasing = TRUE) %>% head(20)
```

@@

```{r}
dfmat116 <- dfm(corpus_subset(corp, Congress == 116), remove = stopwords("english"), remove_punct = TRUE) %>%
    dfm_trim(min_termfreq = 1)

textplot_wordcloud(dfmat116, max_words = 300)

@@

```{r}
dfmat117 <- dfm(corpus_subset(corp, Congress == 117), remove = stopwords("english"), remove_punct = TRUE) %>%
    dfm_trim(min_termfreq = 1)

textplot_wordcloud(dfmat117, max_words = 300)

#Wordcloud comparing Democrats and Republicans
```{r}
dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Party) %>%
    dfm_trim(min_termfreq = 3)

@@

#Wordcloud comparing Congresses
```{r}
dfmatCon <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Congress) %>%
    dfm_trim(min_termfreq = 3)

@@

## Creating document feature matrix
```{r}
dfmat <- df$Summary %>%
  tokens(remove_punct = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  dfm()
```

## Most common words
```{r}
#Overall most common words

tfreq <- dfmat %>%
  textstat_frequency() %>%
  head(20)

@@

ggplot(tfreq, aes(x=frequency, y=feature)) +
geom_col() + 
  theme_minimal()
```

```{r}
# Most common words by Congressional sesson
df_116 <- df %>%
  filter(Congress == "116")

df_117 <- df %>%
  filter(Congress == "117")

dfmat_116 <- df_116$Summary %>%
  tokens(remove_punct = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  dfm()

dfmat_117 <- df_117$Summary %>%
  tokens(remove_punct = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  dfm()

@@

@@

tfreq_116$feature <- factor(tfreq_116$feature, levels=tfreq_116$feature) 
tfreq_117$feature <- factor(tfreq_117$feature, levels=tfreq_117$feature)

p116 <- ggplot(tfreq_116, aes(x=frequency, y=feature)) +
  geom_col() + 
  theme_minimal()

p117 <- ggplot(tfreq_117, aes(x=frequency, y=feature)) +
  geom_col() + 
  theme_minimal()

p116
```

```{r}
p117
```

```{r}
df$era <- ifelse(df$Congress == 116, "Pre", "Post")

ytfreq <- dfmat %>% 
  textstat_frequency(groups = df$era) %>%
  pivot_wider(id_cols=feature, names_from=group, values_from=frequency)

ggplot(ytfreq, aes(x="Post", y="Pre")) + 
  geom_point() +
  coord_fixed()
```
```{r}
sims <- textstat_simil(dfmat, method="cosine")

@@

sim_df
```
```{r}
library(uwot)

corp <- corpus(df$Summary)

@@

colordict <- c( "Labour"="red","LibDems"="yellow", "Conservatives"="Blue","Greens"="green")

p <- ggplot(df, aes(x, y, fill=party)) + 
  geom_point(color="grey", shape=21, size=0.5) + 
  scale_fill_manual(values=colordict) + theme_bw() +
  coord_fixed()

@@

```{r}
library(topicmodels) 
lda <- LDA(dfmat, 3)

lda
```
```{r}
library(tidytext)

@@

text_tokens <- tidy(dfmat) %>% 
  inner_join(lex, by=c("term" = "word"))

doc_sentiments <- tidy(dfmat) %>% 
  inner_join(lex, by=c("term" = "word")) %>% 
  mutate(value=value*count) %>% 
  group_by(document) %>%
  summarise(value = sum(value))

>>>>

```{r}
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
```

@@

##Creatung a dfm from the corpus
```{r }
dfm_corp <- corp %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm()

#Do we also want to lemmatize and apply word stems??

# tokens_replace(pattern = lexicon::hash_lemmas$token, replacement = lexicon::hash_lemmas$lemma) %>%

# tokens_wordstem() %>%
```

##Most common words in the corpus
```{r }
dfm_corp %>% colSums() %>% sort(decreasing = TRUE) %>% head(20)
```
#Wordcloud congress 115

```{r }
dfmat115 <- dfm(corpus_subset(corp, session == 115), remove = stopwords("english"), remove_punct = TRUE,
                remove_numbers = TRUE) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
    dfm_trim(min_termfreq = 1)

textplot_wordcloud(dfmat115, max_words = 300)
```

@@

```{r }
dfmat116 <- dfm(corpus_subset(corp, session == 116), remove = stopwords("english"), remove_punct = TRUE, 
                remove_numbers = TRUE) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
    dfm_trim(min_termfreq = 1)

textplot_wordcloud(dfmat116, max_words = 300)
```

@@

```{r }
dfmat117 <- dfm(corpus_subset(corp, session == 117), remove = stopwords("english"), remove_punct = TRUE,
                remove_numbers = TRUE) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
    dfm_trim(min_termfreq = 1)

textplot_wordcloud(dfmat117, max_words = 300)
```

#Wordcloud comparing Democrats and Republicans
```{r }
#Need to get sponser party data

dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Party) %>%
    dfm_trim(min_termfreq = 3)

@@

#Wordcloud comparing Congresses
```{r }
dfmatCon <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Congress) %>%
    dfm_trim(min_termfreq = 3)

@@

## Most common words (overall)
```{r}
#Overall most common words

tfreq <- dfm_corp %>%
  textstat_frequency() %>%
  head(20)

@@

ggplot(tfreq, aes(x=frequency, y=feature)) +
geom_col() + labs(title="Feature (word) frequency",
        x ="Frequency", y = "Feature") +
  theme_minimal() 
```
## Most common words (by session)

```{r }
# Most common words by Congressional session 115
df_115 <- df %>%
  filter(session == "115")

dfmat_115 <- df_115$summary %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm()

tfreq_115 <- dfmat_115 %>%
  textstat_frequency() %>%
  head(20)

tfreq_115$feature <- factor(tfreq_115$feature, levels=tfreq_115$feature)

ggplot(tfreq_115, aes(x=frequency, y=feature)) +
  geom_col() + labs(title="Feature (word) frequency for 115 session (2017 - 2018)",
        x ="Frequency", y = "Feature") +
  theme_minimal()
```

```{r }
# Most common words by Congressional session 116
df_116 <- df %>%
  filter(session == "116")

dfmat_116 <- df_116$summary %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm()

@@

tfreq_116$feature <- factor(tfreq_116$feature, levels=tfreq_116$feature)

ggplot(tfreq_116, aes(x=frequency, y=feature)) +
  geom_col() + labs(title="Feature (word) frequency for 116 session (2019 - 2020)",
        x ="Frequency", y = "Feature") +
  theme_minimal()
```

```{r}
# Most common words by Congressional session 117
df_117 <- df %>%
  filter(session == "117")

dfmat_117 <- df_117$summary %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm()

@@

tfreq_117$feature <- factor(tfreq_117$feature, levels=tfreq_117$feature)

ggplot(tfreq_117, aes(x=frequency, y=feature)) +
  geom_col() + labs(title="Feature (word) frequency for 117 session (2021 - 2022)",
        x ="Frequency", y = "Feature") +
  theme_minimal()
```

```{r}
df$era <- ifelse(df$session == 116, "Pre", "Post")

ytfreq <- dfm_corp %>% 
  textstat_frequency(groups = df$era) %>%
  pivot_wider(id_cols=feature, names_from=group, values_from=frequency)

ggplot(ytfreq, aes(x="Post", y="Pre")) + 
  geom_point() +
  coord_fixed()
```

```{r}
sims <- textstat_simil(dfm_corp, method="cosine")

@@

sim_df
```

```{r }
df <- df %>%
  mutate(partisan = ifelse(cosponsor_D_perc > 0.5,"Dem", 
                       ifelse(cosponsor_D_perc < 0.5,"Rep",
                              ifelse(cosponsor_D_perc == 0.5,"Neutral", NA))))

corp <- corpus(df$summary)

@@

colordict <- c( "Dem"="blue","Rep"="red", "Neutral"="yellow")

p <- ggplot(df, aes(x, y, fill=partisan)) + 
  geom_point(color="grey", shape=21, size=0.5) + 
  scale_fill_manual(values=colordict) +
  theme_bw() +
  coord_fixed()

@@

##Topic modeling

```{r }
lda <- LDA(dfmat, 3)

lda
```

```{r}
library(tidytext)

@@

text_tokens <- tidy(dfm_corp) %>% 
  inner_join(lex, by=c("term" = "word"))

doc_sentiments <- tidy(dfm_corp) %>% 
  inner_join(lex, by=c("term" = "word")) %>% 
  mutate(value=value*count) %>% 
  group_by(document) %>%
  summarise(value = sum(value))
